\textbf{\sffamily\Huge \ShortTitle}\\ {\textbf{\sffamily\Large \FullTitle}} \vspace{1cm}

### 2015-01-08 proposal/sections/implication-risk.tex
add risks to tex file.

\note{
\begin{itemize}
\item {\em Length: 1-2 pages}
\item Importance of the expected results for the discipline
	\begin{itemize}
	\item     To what extent does the proposed research address important challenges?
	\end{itemize}
\item Importance of the expected results for other areas
\item What are possible risks of the project and how can they be alleviated?
	\begin{itemize}
	\item     What factors could lead to a failure of the project?
	\item     Which factors or persons could support the project and increase the chance for success?
	\item     What if important team members leave the project?
	\end{itemize}
\end{itemize}
}

>>>>

\subsection*{implications}

\subsection*{Risks}

\subsubsection*{Less money}
\begin{itemize}
 \item Description: Get less money to realize the project than defined in the cost accounting.
 \item Solution: Our project is calculated tightly. So we must revalidate the hole project and create a new proposal with less features and workpackages.
\end{itemize}

\subsubsection*{More money needed}
\begin{itemize}
 \item Description: The project needs more money than defined in the cost accounting.
 \item Solution: Looking for new investors to get more money. Sell knowhow to other companies or research groups.
\end{itemize}

\subsubsection*{Less time for research}
\begin{itemize}
 \item Description: The brain waves research needs more time than supposed.
 \item Solution: Buy knowhow from other companies and research groups. Get extern experts to increase the research.
\end{itemize}

\subsubsection*{Team members leave}
\begin{itemize}
 \item Description: One or more team members leave the project.
 \item Solution: All work topics have two members. To avoid loosing knowlegde, there are meetings every week to beware it. After knowlegde about leaving a team member, we are looking for a new team member.
\end{itemize}

\subsubsection*{Brain waves location}
\begin{itemize}
 \item  Description: It is not possible to detect brain waves in the near of the ear.
 \item Solution: We are using sensors to detect brain waves at the forehead.
\end{itemize}

\subsubsection*{Brain waves detection}
\begin{itemize}
 \item Description: It is not possible to detect uniqueness of brain waves.
 \item Solution: It is not possible to continue, because this is the base of the project.
\end{itemize}
